Data Preparation

### 2025-08-16 code/05_data_cleaning.Rmd
Results comments addressed (initial stage).. continue results and discussion
Added data, code, model and figures

Whichever between Cyanistes caeruleus and Parus major is higher.. assign that..

@@

## And now
unique(dataset_after_cleaning$proxy_decision)
```

>>>>

@@

## And now
unique(dataset_after_cleaning$proxy_decision)

## Ensuring all names for risk of bias meta-regression are clean

unique(dataset_after_cleaning$blinding)

dataset_after_cleaning <- dataset_after_cleaning %>%
  mutate(blinding = case_when(
    blinding == "no" ~ "n",
    TRUE ~ blinding
  ))

## And now
unique(dataset_after_cleaning$blinding)
## all good, works!

## And now for missing data
unique(dataset_after_cleaning$missing_data)

dataset_after_cleaning <- dataset_after_cleaning %>%
  mutate(missing_data = case_when(
    missing_data == "no" ~ "n",
    missing_data == "yes" ~ "y",
    TRUE ~ missing_data
  ))

## And now
unique(dataset_after_cleaning$missing_data)
# Gooood!

## Last one is 
unique(dataset_after_cleaning$random_assignment)

dataset_after_cleaning <- dataset_after_cleaning %>%
  mutate(random_assignment = case_when(
    random_assignment == "no" ~ "n",
    random_assignment == "yes" ~ "y",
    TRUE ~ random_assignment
  ))

# And now?
unique(dataset_after_cleaning$random_assignment)

## Good good, all looks well now!
```

### 2025-08-16 code/06_data_preparation.Rmd
Added data, code, model and figures

# Setting up workspace

pacman::p_load(here, tidyverse, dplyr, stringr, metafor, orchaRd,ggpubr,ggrepel) #Packages needed

@@

      # Madrid Region
      str_detect(population_ID, regex("madrid|manzanares|villalba|soto del real|central spain", ignore_case = TRUE)) ~ "Madrid Province, Spain",

@@

```{r}
# 9 from GNM_355 where repeated estimates over days for haemoglobin are present and I cannot combine them as I did for chick mass over months.. since the sample is the same and these are the repeated measures of the same sample.
noSMDH=dataset_analysis%>%filter(is.na(SMDH))
```

>>>>

# Setting up workspace
if (!requireNamespace("pacman", quietly = TRUE)) {
  install.packages("pacman")
}
pacman::p_load(here, tidyverse, dplyr, stringr, metafor, orchaRd,ggpubr,ggrepel) #Packages needed

@@

      # Madrid Region
      str_detect(population_ID, regex("madrid|manzanares|villalba|soto del real", ignore_case = TRUE)) ~ "Madrid Province, Spain",

@@

```{r}
# 9 from GNM_355 where repeated estimates over days for haemoglobin are present and I cannot combine them as I did for chick mass over months.. since the sample is the same and these are the repeated measures of the same sample.
low_sample=dataset_analysis%>%filter(is.na(SMDH))
write.csv(low_sample,file=here::here("data/03_data_cleaning/low_sample.csv"),row.names = FALSE)
```

This is very very low sample size, it makes no sense to keep them. I will exclude them from all the further analysis.

```{r}
dataset_analysis<-dataset_analysis%>%anti_join(low_sample,by="Observation_ID")
```
